BIOL 274 Homework 7

### 2024-03-29 bio_dynamics/bio274_hw7.Rmd
phase plane

```{r, echo=FALSE, results='hide'}
fun2 <- c(dx ~ x+2*y, dy ~3*x+2*y)
p1 <- phaseplane(fun2,x_var="x",y_var="y", x_window = c(-7, 7), y_window = c(-7, 7))

@@

y2 <- tibble(x=c(0,0,-6,5,0), y=c(1,4,1,0.5,-3), IC=c("V1", "V2", "V3", "V4", "V5"))%>% mutate(pt = paste0("(",x, ",", y, ")"))
```

@@

z <- left_join(x,y) %>% filter(x<7 & x>-7 & y<7 & y>-7) %>% left_join(y2 %>% select(IC, pt), by="IC")

@@

```{r}
p1+theme_classic()+
  geom_abline(slope=-1, color="gray", linewidth=1)+
  geom_abline(slope=3/2, color="gray", linewidth=1)+
  geom_path(data=z, aes(x=x, y=y, color=pt), linewidth=1.5)+
  geom_point(data=y2, aes(x=x,y=y, color=pt), shape=21, fill="white",size=5, stroke=2)+labs(color="IC")

>>>>

```{r, echo=FALSE, results='hide'}
fun2 <- c(dx ~ x+2*y, dy ~3*x+2*y)

p1 <- phaseplane(fun2, x_var="x" ,y_var="y", x_window = c(-7, 7), y_window = c(-7, 7))

@@

y0_df <- tibble(x=c(0,0,-6,5,0), y=c(1,4,1,0.5,-3), IC=c("V1", "V2", "V3", "V4", "V5"))%>% mutate(pt = paste0("(",x, ",", y, ")"))
```

@@

z <- left_join(x,y) %>% filter(x<7 & x>-7 & y<7 & y>-7) %>% left_join(y0_df %>% select(IC, pt), by="IC")

@@

```{r}
p1+theme_classic()+
  geom_abline(slope=-1, color="gray", linewidth=1)+
  geom_abline(slope=3/2, color="gray", linewidth=1)+
  geom_path(data=z, aes(x=x, y=y, color=pt), linewidth=1.5)+
  geom_point(data=y2, aes(x=x,y=y, color=pt), shape=21, fill="white",size=4, stroke=2)+labs(color="IC")
